RADseq Works in Primates, Dammit.

### 2012-12-09 paper/paper.tex
Started on results section in paper

	Genomic DNA from 6 animals was digested with \emph{PspXI} (New England Biolabs) and used to create a multiplexed RAD tag library. Our library preparation method followed that of Etter et al, 2011 with the following modifications: the P1 adapter top\textcolor{red}{(?)} oligonucleotide was modified to have an overhang corresponding to the cut site of \emph{PspXI}, and a longer P2 adapter suitable for paired end sequencing was used (P2\_top: 5'-\textcolor{red}{SEQUENCEHERE}-3'; P2\_bottom: 5'-\textcolor{red}{SEQUENCEHERE}-3'). Individual-specific barcodes contained in the P1 adapter differed by at least \textcolor{red}{three} nucleotides. We chose \emph{PspXI} based on the results of \emph{in silico} digestion of the human, rhesus macaque, and baboon reference genomes using custom Perl scripts (\textcolor{red}{refs}). We sequenced the prepared library as one 150-cycle paired-end run of an Illumina MiSeq at the NYU Langone Medical Center's Genome Technology Center using a spike-in of 30\% PhiX DNA to control for low diversity in the library at the barcode and restriction sites. Sequences are available to download from the NCBI Short Read Archive (accession number \textcolor{red}{SRAXXXXXX.X}).

\begin{table}[h]
\caption{Samples}
\begin{center}
  \begin{tabular}{ l | l | l }
    \hline
    Taxon & Source & Geographic Locality \\ \hline\hline
    \textcolor{red}{Langur?} & NYU Collection & Unknown \\ \hline
    \emph{Allenopithecus nigroviridis} & NYU Collection & Unknown \\ \hline
    \emph{Macaca mulatta} & NYU Collection & Unknown \\ \hline
    \emph{Cercocebus torquatus atys} & NYU Collection & Unknown \\ \hline
    \emph{Papio anubis\textcolor{red}{?}} & NYU Collection & Unknown \\ \hline
    \emph{Theropithecus gelada} & NYU Collection & Unknown \\ 
    \hline
  \end{tabular}
\end{center}
\end{table}

@@

	After performing local realignment around indels with GATK (\textcolor{red}{ref}), SNPs and short indels were identified using SAMtools mpileup and BCFtools (\textcolor{red}{ref}). A minimum coverage of 3 reads and a maximum of 100 was required to call a SNP or an indel at a given location.

	To analyze the degree of overlap between multiplexed individual's datasets, we...

\paragraph{Analysis Pipeline - Analysis of Degree of Overlap}
\begin{itemize}
	\item Calculate coverage of restriction site-associated regions
	\begin{itemize}
		\item Info on targeted intervals
		\begin{itemize}
			\item Total number possible targets in rhesus genome (compare to human too?)
			\item Total possible target BP
		\end{itemize}
		\item How many targets did we hit?
		\begin{itemize}
			\item BEDtools multiBamCoverage for this job
			\item Number and percentage of targets with coverage $\ge 1$
			\item Number and percentage of targets with coverage $\ge N$
		\end{itemize}
	\end{itemize}
	\item Count orthologous SNPs shared between individuals
	\begin{itemize}
		\item VCFtools vcf-compare for this job
	\end{itemize}
\end{itemize}

@@

\section{Results}
\begin{itemize}
	\item Info from analyzing reads with FastQC
	\begin{itemize}
		\item Number of reads (per ind. too see table)
		\item Total sequence bp (per ind. too see table)
		\item Maximum possible sequence depth (Cut?)
		\item Other stats that FastQC gives you?
	\end{itemize}
	\item Table: 
	\begin{itemize}
		\item Number of reads per animal
		\item Total sequenced bp per animal?
		\item Number that passed filtration
		\item Number of loci hit
		\item Number of loci hit with coverage $\ge N$
		\item Number of SNPs
	\end{itemize}
	\item SNP info from merged analysis
	\item SNP Venn diagram?
	\item Table of overlapping region, orthologous SNP counts
	%\item Phylogenetic tree
\end{itemize}

>>>>

	Genomic DNA from 6 primates was digested with \emph{PspXI} (New England Biolabs) and used to create a multiplexed RAD tag library. Our library preparation method followed that of Etter et al, 2011 with the following modifications: the P1 adapter top\textcolor{red}{(?)} oligonucleotide was modified to have an overhang corresponding to the cut site of \emph{PspXI}, and a longer P2 adapter suitable for paired end sequencing was used (P2\_top: 5'-\textcolor{red}{SEQUENCEHERE}-3'; P2\_bottom: 5'-\textcolor{red}{SEQUENCEHERE}-3'). Individual-specific barcodes contained in the P1 adapter differed by at least \textcolor{red}{three} nucleotides. We chose \emph{PspXI} based on the results of \emph{in silico} digestion of the human, rhesus macaque, and baboon reference genomes using custom Perl scripts (\textcolor{red}{refs}). We sequenced the prepared library as one 150-cycle paired-end run of an Illumina MiSeq at the NYU Langone Medical Center's Genome Technology Center using a spike-in of 30\% PhiX DNA to control for low diversity in the library at the barcode and restriction sites. Other individuals were sequenced alongside those of the present study. Sequences are available to download from the NCBI Short Read Archive (accession number \textcolor{red}{SRAXXXXXX.X}).

@@

	After performing local realignment around indels with GATK (\textcolor{red}{ref}), SNPs and short indels were identified using SAMtools mpileup and BCFtools (\textcolor{red}{ref}). A minimum coverage of 3 reads and a maximum of 100 was required to call a SNP or an indel at a given location. Orthologous SNPs were tallied using VCFtools (\textcolor{red}{ref}).

	To assess how many restriction sites were successfully sequenced and to analyze the degree of overlap between multiplexed individual's datasets, we first found all possible \emph{PspXI} cut sites using the oligoMatch utility in the USCS Genome Browser program (\textcolor{red}{ref}). This allowed us to calculate the coverage of these restriction site-associated regions using BEDtools' multiBamCov program (\textcolor{red}{ref}).

@@

\section{Results}

% 3804227030 bp total (12,983,710 pairs of reads * (142bp + 151bp). This includes non-OWM taxa, remember.
% OWM sequencing reads: 6,125,860 total, half that many pairs
% Of those, 2029586 passed the filtration steps

6.1 million sequencing reads with an intact barcode and restriction enzyme cut site could be assigned confidently to one of the six Old World monkeys in the present study. Roughly 2.0 million of those reads were successfully mapped to the rhesus macaque genome and passed all quality control filtration steps. Relative to the reference genome, our study identified 531,175 SNPs and 24,260 small indels among all samples. Information for each individual is summarized in Table 1.

In the rhesus macaque genome, we found 108,727 possible cut sites for \emph{PspXI}.

\begin{table}[h]
\caption{Individual Sample Information}
\begin{center}
	\small
	\begin{tabular}{ p{3cm} || l || p{1.75cm} | p{1.75cm} || p{1.75cm} | p{1.75cm} | l }
		\hline
		Taxon & Source & \# Reads & \# Filtered Reads & \# Loci $\ge 1$ Read & \# Loci $\ge 3$ Reads & \# SNPs \\ \hline\hline
		\textcolor{red}{Langur?} & \textcolor{red}{Unknown} & 1,367,050 & 306,248 & & & 363,501 \\ \hline
		\emph{Allenopithecus nigroviridis} & \textcolor{red}{Unknown} & 1,325,558 & 447,279 & & & 356,750 \\ \hline
		\emph{Macaca mulatta} & \textcolor{red}{Unknown} & 481,376 & 234,659 & & & 279,350 \\ \hline
		\emph{Cercocebus torquatus atys} & \textcolor{red}{Unknown} & 297,290 & 124,700 & & & 319,766 \\ \hline
		\emph{Papio anubis\textcolor{red}{?}} & \textcolor{red}{Unknown} & 743,556 & 313,676 & & & 316,118 \\ \hline
		\emph{Theropithecus gelada} & \textcolor{red}{Unknown} & 1,911,030 & 603,024 & & & 366,097 \\
		\hline
	\end{tabular}
\end{center}
\end{table}

\begin{itemize}
	\item Number of loci hit
	\item Number of loci hit with coverage $\ge N$
	\item SNP info from merged analysis
	\item SNP Venn diagram?
	\item Calculate coverage of restriction site-associated regions
	\item Total number possible targets in rhesus genome (compare to human too?)
	\item Total possible target BP
	\item How many targets did we hit?
	\item BEDtools multiBamCoverage for this job
	\item Number and percentage of targets with coverage $\ge 1$
	\item Number and percentage of targets with coverage $\ge N$
	\item Count orthologous SNPs shared between individuals
	\item VCFtools vcf-compare for this job
\end{itemize}
